Three-Dimensional Confocal Raman Temperature Characterization of Electrokinetically Pumped Microchannels

### 2018-12-14 paper.tex
paper final, subido a MicroFluidics and Nanofluidics

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{guillermobrinatti@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
              \and
              Juan Martin Cabaleiro \at
           Laboratorio de Fluidodinámica, FIUBA, CONICET, Av. Paseo Colón 850, Buenos Aires, Argentina, and Laboratorio de Micro y Nanofluídica y Plasmas, UdeMM, Av. Rivadavia 2258, Buenos Aires, Argentina  \\
              Tel.: +54 11 5285 0467\\              
              \email{jmcabaleiro@gmail.com}  
}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/setup.eps}
\caption{Schematic representation of the confocal microscope used for Raman thermometry of water. A 405~nm single mode fiber coupled laser is used as excitation beam. The beam is focused in the sample by using a 40X microscope objective which also collects the Raman emission. A dichroic mirror (420~LP) is used to separate the signal which is then focused on a multimode optical fiber to achieve confocal resolution. The other end of the fiber enters a specially designed spectrometer which divide the Raman spectrum in two detectors for later processing. A different wavelength (520 nm) is used to get a scattering image of the sample which is separated from the signal and the pump beam by means of a dichroic mirror (505~LP) and sent to a CMOS camera. Colored arrows indicate the wavelength and the propagation direction of each beam.\label{fig:setup}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/spectra.eps}
\caption{Raman spectra of water at different temperatures. A dashed line marks the isosbestic point. At shorter wavelengths the signal decreases with rising temperature. At longer wavelengths the opposite behavior occurs. Shaded regions indicate the portion of the spectrum collected in each detector in the temperature measurements as shown in figure \ref{fig:setup}.\label{fig:spectra}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/calib.eps}
\caption{Temperature signal $S$ as a function of the water sample temperature. A linear fit is used as calibration for the method. Dispersion around the linear fit gives a temperature resolution of $\Delta T = 0.8$ K.\label{fig:calib}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/temporal.eps}
\caption{Temperature rise at turn on for a microchannel under elecroosmotic flow. Electric field is activated at $t=0$. Two different positions 5 mm apart show the same behavior. The position $x=0$ is set at the inlet reservoir. (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 20~mm).\label{fig:temporal}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/horizontal.eps}
\caption{Horizontal scan (perpendicular to the flow, parallel to the coverglass) showing a constant temperature rise across the channel (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 40~mm).\label{fig:horizontal}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/vertical.eps}
\caption{Two vertical scans at different dissipated powers in the same channel used in figure \ref{fig:horizontal}. Position zero corresponds to the center of the channel. On the right side lays the coverglass.\label{fig:vertical}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/long.eps}
\caption{Longitudinal scan across a L = 20~mm channel. The experiment show a constant temperature rise around 13~K.\label{fig:long}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/rectas.eps}
\caption{Temperature rise as a function of dissipated power per unit glass area on four different channel geometries. A linear fit is performed in each data set in order to compare the slope corresponding to each channel. The similarity between the lines seems to indicate that the glass floor of the channel dominates as dissipation mechanism. Ref er to table 1 for channel dimensions.\label{fig:rectas}}
\end{figure}

>>>>

\institute{Guillermo D. Brinatti Vazquez \at
              Laboratorio de Fotónica, FIUBA, Av. Paseo Colón 850, Buenos Aires, Argentina y Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET). \\
              Tel.: +54 11 5285 0828\\
              \email{guillermobrinatti@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Oscar E. Martínez \at
              Laboratorio de Fotónica, FIUBA, Av. Paseo Colón 850, Buenos Aires, Argentina y Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET).\\
              \email{omartinez@fi.uba.ar}
              \and
              Juan Martin Cabaleiro \at
           Laboratorio de Fluidodinámica, FIUBA, CONICET, Av. Paseo Colón 850, Buenos Aires, Argentina, and Laboratorio de Micro y Nanofluídica y Plasmas, UdeMM, Av. Rivadavia 2258, Buenos Aires, Argentina  \\
              Tel.: +54 11 5285 0467\\              
              \email{jmcabaleiro@gmail.com}  
}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig1.eps}
\caption{Schematic representation of the confocal microscope used for Raman thermometry of water. A 405~nm single mode fiber coupled laser is used as excitation beam. The beam is focused in the sample by using a 40X microscope objective which also collects the Raman emission. A dichroic mirror (420~LP) is used to separate the signal which is then focused on a multimode optical fiber to achieve confocal resolution. The other end of the fiber enters a specially designed spectrometer which divide the Raman spectrum in two detectors for later processing. A different wavelength (520 nm) is used to get a scattering image of the sample which is separated from the signal and the pump beam by means of a dichroic mirror (505~LP) and sent to a CMOS camera. Colored arrows indicate the wavelength and the propagation direction of each beam.\label{fig:setup}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig2.eps}
\caption{Raman spectra of water at different temperatures. A dashed line marks the isosbestic point. At shorter wavelengths the signal decreases with rising temperature. At longer wavelengths the opposite behavior occurs. Shaded regions indicate the portion of the spectrum collected in each detector in the temperature measurements as shown in figure \ref{fig:setup}.\label{fig:spectra}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig3.eps}
\caption{Temperature signal $S$ as a function of the water sample temperature. A linear fit is used as calibration for the method. Dispersion around the linear fit gives a temperature resolution of $\Delta T = 0.8$ K.\label{fig:calib}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig4.eps}
\caption{Temperature rise at turn on for a microchannel under elecroosmotic flow. Electric field is activated at $t=0$. Two different positions 5 mm apart show the same behavior. The position $x=0$ is set at the inlet reservoir. (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 20~mm).\label{fig:temporal}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig5.eps}
\caption{Horizontal scan (perpendicular to the flow, parallel to the coverglass) showing a constant temperature rise across the channel (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 40~mm).\label{fig:horizontal}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig6.eps}
\caption{Two vertical scans at different dissipated powers in the same channel used in figure \ref{fig:horizontal}. Position zero corresponds to the center of the channel. On the right side lays the coverglass.\label{fig:vertical}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig7.eps}
\caption{Longitudinal scan across a L = 20~mm channel. The experiment show a constant temperature rise around 13~K.\label{fig:long}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/fig8.eps}
\caption{Temperature rise as a function of dissipated power per unit glass area on four different channel geometries. A linear fit is performed in each data set in order to compare the slope corresponding to each channel. The similarity between the lines seems to indicate that the glass floor of the channel dominates as dissipation mechanism. Ref er to table 1 for channel dimensions.\label{fig:rectas}}
\end{figure}
